This PDF is a Git Repository\\Containing its Own \LaTeX\ Source\\and a Copy of Itself

### 2017-05-28 article.tex
Added a suggestion at the end
If you're going to "fake" output, at least make sure it's sorted properly!
Fixed a misspelling

\begin{center}
\begingroup
\setbox9=\hbox{\footnotesize\verb|Receiving objects: 100% (174/174), 103.48 KiB | 0 bytes/s, done.|}
\begin{minipage}{\wd9}
\footnotesize\begin{verbatim}
$ git clone article.pdf foo
Cloning into 'foo'...
Receiving objects: 100% (174/174), 103.48 KiB | 0 bytes/s, done.
Resolving deltas: 100% (100/100), done.
$ cd foo
$ ls
article.tex
article.pdf
\end{verbatim}
\end{minipage}
\endgroup
\end{center}

@@

\begin{center}
\begin{tikzpicture}
\node at (0,0) (text) {\begin{minipage}{0.8\hsize}\small
As a matter of fact, G-d just questioned my judgement. He said,
`Terry, are you worthy to be the man who makes The Temple? If you are,
you must answer: Is this [dastardly], or is this divine intellect?'
\end{minipage}};
\node[anchor=north east] at (text.north west) {\LARGE``};
\node[anchor=south west] at (text.south east) {\LARGE''};
\node[anchor=north east] at (text.south east) (terry) {\setbox9=\hbox{\llap{---}Terry A.\ Davis, creator of TempleOS}\parbox{\wd9}{\raggedright\box9 self-proclaimed ``smartest programmer that's ever lived''}};
\end{tikzpicture}
\end{center}

@@

This PDF is a git bundle containing its \LaTeX\ source, as well as all
of the code necessary to regenerate this polyglot.

>>>>

\begin{center}
\begingroup
\setbox9=\hbox{\footnotesize\verb|Receiving objects: 100% (174/174), 103.48 KiB | 0 bytes/s, done.|}
\begin{minipage}{\wd9}
\footnotesize\begin{verbatim}
$ git clone article.pdf foo
Cloning into 'foo'...
Receiving objects: 100% (174/174), 103.48 KiB | 0 bytes/s, done.
Resolving deltas: 100% (100/100), done.
$ cd foo
$ ls
article.pdf article.tex
\end{verbatim}
\end{minipage}
\endgroup
\end{center}

@@

\begin{center}
\begin{tikzpicture}
\node at (0,0) (text) {\begin{minipage}{0.8\hsize}\small
As a matter of fact, G-d just questioned my judgment. He said,
`Terry, are you worthy to be the man who makes The Temple? If you are,
you must answer: Is this [dastardly], or is this divine intellect?'
\end{minipage}};
\node[anchor=north east] at (text.north west) {\LARGE``};
\node[anchor=south west] at (text.south east) {\LARGE''};
\node[anchor=north east] at (text.south east) (terry) {\setbox9=\hbox{\llap{---}Terry A.\ Davis, creator of TempleOS}\parbox{\wd9}{\raggedright\box9 self-proclaimed ``smartest programmer that's ever lived''}};
\end{tikzpicture}
\end{center}

@@

This PDF is a git bundle containing its \LaTeX\ source, as well as all
of the code necessary to regenerate this polyglot. Clone it to take a
look at the history of this document and its associated code!
